---
title: "lecture_7_class_walkthrough"
author: "LQ"
date: "4/24/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##More on function writing
##First we will revisit our function from last day

```{r}
source("http://tinyurl.com/rescale-R")

```

```{r}
library(ggplot2)
```

Test rescale function
```{r}
str(rescale)
```

```{r}
rescale(1:10)

```


```{r}
x <- c(1:10, "string")
!is.numeric(x)
```


##Function practice
Write a function to identify NA elements in two vectors
Start with a simple example input where I know what the answer shuld be.

```{r}
x <- c( 1, 2, NA, 3, NA) 
y <- c(NA, 3, NA, 3, 4)

is.na(x)
is.na(y)
```


I am looking for the positions where it is TRUE in both vectors
```{r}
is.na(x) & is.na(y)
```

Use sum to find out how many trues there are 
```{r}
sum(is.na(x) & is.na(y))


```

THIS IS MY WORKING SNIPPET OF CODE

```{r}
both_na <- function(x,y) {
  sum(is.na(x) & is.na(y))
}
```

```{r}
both_na(x,y)
```
```{r}
both_na(c(NA, NA, NA), c(NA, NA,1))
```

```{r}
both_na(c(NA, NA, NA), c(1, NA, NA, NA))
```
It gives back a number because R is recycling the vector so going back to the beginning of the shorter vector to make the "n's" the same
```{r}
both_na(c(NA, NA, NA), c(1, NA, NA, NA, NA, NA))
```

Check the length of our inputs are equal
```{r}
x<- c(NA, NA, NA)
y <-c(1, NA, NA, NA, NA, NA)
length(x) != length(y)
```

```{r}
both_na3 <- function(x, y) {
  ## Check for NA elements in both input vectors and don't allow re-cycling 
  if(length(x) != length(y)) {
    stop("Input x and y should be vectors of the same length", call.=FALSE)
  }
  sum( is.na(x) & is.na(y) )
}


```

Try theboth_na3() function with extra features

```{r}
x <- c(1, 2, NA, 3, NA)
y <- c(NA, 3, NA, 3, NA)
both_na3(x,y)
```


```{r}
x <- c(100, 100, 100, 100, 100, 100, 100, 90)
(sum(x)-min(x)) / (length(x)-1)

y <- c(100, NA, 90, 90, 90, 90, 97, 80)
mean(y, na.rm = TRUE)
```


```{r}
x <- c(100, 100, 100, 100, 100, 100, 100, 90)
(sum(x)-min(x)) / (length(x)-1)

y <- c(100, NA, 90, 90, 90, 90, 97, 80)
mean(y, na.rm = TRUE)
```

```{r}
grade <- function(x) {
  (sum(x)-min(x)) / (length(x)-1)
}
grade(x)
```

```{r}
grade_2 <- function(y) {
  (sum(y, na.rm = T)-min(y, na.rm = T)) / (length(y)-1)
}
grade_2(y)
```
```{r}
y <- c(100, NA, 90, 90, 90, 90, 97, 80)
grade_2 <- function(y) {
  (sum(y,na.rm = T)-min(y, na.rm = T))/(length(y)-1)
}
grade_2(y)
```

```{r}
url <- "https://tinyurl.com/gradeinput"
students<- read.csv(url, row.names = 1)
head(students)
```

```{r}
grade_2(students[5,])
```


```{r}
ans<-apply(students, 1, grade_2)
ans
```

```{r}
sort(ans, decreasing = FALSE)
```


FINDING THE INTERSECTION BETWEEN 2 VECTORS
```{r}
source("http://tinyurl.com/rescale-R")
df1
df2
```


```{r}
x<-df1$IDs
y<-df2$IDs

intersect(x,y)
```

```{r}
x
y

x %in% y
x[x %in% y]
```

```{r}
cbind( x[ x %in% y ], 
       y[ y %in% x ] )
```

```{r}
gene_intersect <- function(x, y) {
  cbind( x[ x %in% y ], y[ y %in% x ] )
}
```

```{r}
gene_intersect(x,y)
```

```{r}
gene_intersect2 <- function(df1, df2) { 
   cbind( df1[ df1$IDs %in% df2$IDs, ], 
          df2[ df2$IDs %in% df1$IDs, "exp"] )
}

gene_intersect2(df1, df2)
```



```{r}
gene_intersect4 <- function(df1, df2, gene.colname="IDs") { 

  df1.name <- df1[,gene.colname]
  df2.name <- df2[,gene.colname]

  df1.inds <- df1.name %in% df2.name
  df2.inds <- df2.name %in% df1.name

   cbind( df1[ df1.inds, ], 
          exp2=df2[ df2.inds, "exp"] )
}

gene_intersect4(df1, df2)
```

```{r}
merge(df1, df2, by="IDs")
```

```{r}
students$IDs <- rownames(students)

ggplot(students, aes(IDs, hw1)) + geom_jitter(height = 2, width = 2)
```


```{r}
ggplot(students, aes(IDs, hw2)) + geom_jitter(height = 2, width = 2)

```
