---
title: "lecture_12_class_walkthrough"
author: "LQ"
date: "5/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
file <- get.pdb("1hsg")
pdb <- read.pdb(file)
pdb
```

```{r}
#Select protein only
prot_sel <- atom.select(pdb, "protein", value = TRUE)
prot_sel
write.pdb(prot_sel, file = "1hsgprotein.pdb")

```



```{r}
#Select ligand only
lig_sel <- atom.select(pdb, "ligand", value = TRUE)
lig_sel
write.pdb(lig_sel, file = "1hsg_ligand.pdb" )
```

#Add Hydrogens and charges in ADT
We opened our protein only PDB file in AutoDoc Tools and added hydrogens and atom-types needed for docking calculations.

##Run docking

We will use AutoDoc Vina here  at the UNIX command line!
The command I used was:
ʻDownloads/autodock_vina_1_1_2_mac/bin/vina --config config.txt

##Process results back in R
```{r}
res <-  read.pdb("all.pdbqt", multi = TRUE)
res
write.pdb(res, file="results.pdb")
```

Compare our docking poses to the MERK drug structure
```{r}
res <- read.pdb("all.pdbqt", multi=TRUE) 
ori <- read.pdb("1hsg_ligand.pdbqt")
rmsd(ori, res)
```




#Normal Mode Analysis Example
NMA
```{r}
library(bio3d)
pdb <- read.pdb("1HEL")
modes <- nma(pdb) 
plot(modes, sse=pdb)
# Visualize NMA results
mktrj(modes, mode=7, file="nma_7.pdb")
```

