---
title: "lecture_11_class_walkthrough"
author: "LQ"
date: "5/8/2019"
output: github_document
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Q1: Download a CSV file from the PDB site (accessible from “Analyze” -> “PDB Statistics” > “by Experimental Method and Molecular Type”. Move this CSV file into your RStudio project and determine the percentage of structures solved by X-Ray and Electron Microscopy. Also can you determine what proportion of structures are protein? Aim to have a rendered GitHub document with working code that yields your answers.*

```{r}
db <- read.csv("Data Export Summary.csv")
head(db)
#View(db)
```

```{r}
#Total number of structures in the PDB database
sum(db$Total)
#rowSums(db[,1:4])
```

```{r}
#Percent of each experimental method
(db$Total/sum(db$Total))*100
```

```{r}
#What percent are protein
(sum(db$Proteins)/sum(db$Total)) *100
```

*Q2: Type HIV in the PDB website search box on the home page and determine how many HIV-1 protease structures are in the current PDB?*
#1157



##Section 3. Using bio3D

Let's read the PDB file we downloaded into R to seehow things live in this place
```{r}
library(bio3d)
```

```{r}
?bio3d()
```

```{r}
pdb <- read.pdb("1hsg.pdb")
pdb

```

```{r}
pdb$seqres
#shortens sequence to amino acid abbreviations
aa321(pdb$seqres)
```

```{r}
attributes(pdb)
```

```{r}
head(pdb$atom)
#print a subset of $atom data for the first 2 atoms
pdb$atom[1:2, c("eleno", "elety", "x","y","z")]
# Note that individual $atom records can also be accessed like this
pdb$atom$elety[1:2]
# Which allows us to do the following
plot.bio3d(pdb$atom$b[pdb$calpha], sse=pdb, typ="l", ylab="B-factor")
```

```{r}
# Print a summary of the coordinate data in $xyz
pdb$xyz
```

```{r}
# Examine the row and column dimensions
dim(pdb$xyz)
# Print coordinates for the first two atom
pdb$xyz[ 1, atom2xyz(1:2) ]
```


##Section 4: atom selection examples

Let's select residue 1
```{r}
inds <- atom.select(pdb, resno = 10)
pdb$atom[inds$atom,]
```

```{r}
atom.select(pdb, resno = 10, value = TRUE)
```

```{r}

pdb_sel <- atom.select(pdb, "protein"  ,value = TRUE)
pdb_sel
write.pdb(pdb_sel, file = "1hsg_protein.pdb")

```

```{r}
lig_sel <- atom.select(pdb, "ligand", value = TRUE)
lig_sel
```

```{r}
write.pdb(lig_sel, file = "1hsg_ligand.pdb")
```

```{r}
#install.packages("devtools")

```

```{r}
#devtools::install_bitbucket("Grantlab/bio3d-view")

```

```{r}
# Load the package
library("bio3d.view")
# view the 3D structure
view(pdb, "overview", col="sse")
```

##Section 6: Working with Multiple PDB Files

```{r}
# Download some example PDB files
ids <- c("1TND_B","1AGR_A","1TAG_A","1GG2_A","1KJY_A","4G5Q_A")
files <- get.pdb(ids, split = TRUE)
```

```{r}
# Extract and align the chains we are interested in
pdbs <- pdbaln(files, fit = TRUE)
# Print to screen a summary of the 'pdbs' object
pdbs
```

```{r}
pdbs_2 <- pdbaln(files)
pdbs_2
```


```{r}
view(pdbs)
view (pdbs_2)
```

*Q8: What effect does setting the fit=TRUE option have in the related rmsd() function? What does RMSD measure and what would the results indicate if you set fit=FALSE or removed this option? HINT: Bio3D functions have various default options that will be used if the option is not explicitly specified by the user, see help(rmsd) for an example and note that the input options with an equals sign (e.g. fit=FALSE) have default values.*

#You want the RMSD to be of the superimposed (fitted) structures otherwise it will be way larger because the non-fitted structures will be more separated from each other (view fit = TRUE and fit = FALSE files)


```{r}
# Access the first 5 rows, and 8 columns
pdbs$ali[1:5, 1:8]
# Associated residues numbers
pdbs$resno[1:5, 1:8]
```

```{r}
# Calculate sequence identity
seqidentity(pdbs)
# Calculate RMSD
rmsd(pdbs)
```

```{r}
# Calculate RMSD
rd <- rmsd(pdbs)
# Clustering 
hc <- hclust(as.dist(rd))
grps <- cutree(hc, k=3)
# Plot results as dendrogram
hclustplot(hc, k=3)
```

```{r}
# Perform PCA
pc.xray <- pca(pdbs)
# Plot our results summary (PCA score plot and scree-plot)
plot(pc.xray)
# Visualize first principal component
pc1 <- mktrj(pc.xray, pc=1, file="pc_1.pdb")
view(pc1)
```


```{r}
# The rglwidget() function from the rgl package will show output in your Rmd notebook and rendered html_output documents
library(rgl) 
view(pc1)
rglwidget()

```

